# Insert chapter 3 logistic regression

*Describe the work you have done this week and summarize your learning.*

- Describe your work and results clearly. 

#3.1 Data wrangling 
```{r}
library(dplyr)
library(ggplot2)

#loading the data & exploring the structure
url <- "http://s3.amazonaws.com/assets.datacamp.com/production/course_2218/datasets"
url_mat <- paste(url, "student-mat.csv", sep = "/")
url_mat
mat <- read.table(url_mat, sep = ";" , header=TRUE)
url_por <- paste(url, "student-por.csv", sep ="/")
url_por
por <- read.table(url_por, sep = ";", header = TRUE)
colnames(mat)
colnames(por)

dim(mat)
str(mat)
dim(por)
str(por)

join_by <- c("school", "sex", "age", "address", "famsize", "Pstatus", "Medu", "Fedu", "Mjob", "Fjob", "reason", "nursery","internet")
math_por <- inner_join(mat, por, by = join_by, suffix = c(".mat", ".por"))
joined_columns <- select(math_por, one_of(join_by))
notjoined_columns <- colnames(mat)[!colnames(mat) %in% join_by]

alc <- select(math_por, one_of(join_by))
notjoined_columns <- colnames(mat)[!colnames(mat) %in% join_by]
notjoined_columns

for(column_name in notjoined_columns) {
  # select two columns from 'math_por' with the same original name
  two_columns <- select(math_por, starts_with(column_name))
  # select the first column vector of those two columns
  first_column <- select(two_columns, 1)[[1]]
  # if that first column vector is numeric...
  if(is.numeric(first_column)) {
    # take a rounded average of each row of the two columns and
    # add the resulting vector to the alc data frame
    alc[column_name] <- round(rowMeans(two_columns))
  } else { # else if it's not numeric...
    # add the first column vector to the alc data frame
    alc[column_name] <- first_column
  }
}

# glimpse at the new combined data
glimpse(alc)

#new variables
alc <- alc %>% 
  mutate(alc_use = (Dalc + Walc)/2) %>% 
  mutate(high_use = alc_use > 2)

#saving the tidied dataset

write.table(alc,file="alc.cvs",sep = ",")
```


#3.2data analysis 

# Read the data file
```{r}
library(tidyr); library(dplyr); library(ggplot2)

#  study the relationships between high alcohol consumption, studytime health，and freetime

#Numerically and graphically explore the distributions of high alcohol consumption, studytime health，and freetime，and their relationships with alcohol consumption

```

```{r}
#Use logistic regression to statistically explore the relationship between choosen variables.
my_model<- glm(formula =high_use ~ health+studytime+freetime,
               family = binomial(link="logit"),
                data = alc)
summary(my_model)
coef(my_model)
```



```{r}
# explore the predictive power of you model.
probabilities <- predict(my_model, type = "response")
# add the predicted probabilities to 'alc'
alc <- mutate(alc, probability = probabilities)
# use the probabilities to make a prediction of high_use
alc <- mutate(alc, prediction = probability > 0.5)

# initialize a plot of 'high_use' versus 'probability' in 'alc'
g <- ggplot(alc, aes(x = probability, y = high_use, col = prediction))

# define the geom as points and draw the plot
g + geom_point()

# tabulate the target variable versus the predictions
table(high_use = alc$high_use, prediction = alc$prediction) %>% prop.table %>% addmargins


```

- Assume the reader has an introductory course level understanding of writing and reading R code as well as statistical methods.


- Assume the reader has no previous knowledge of your data or the more advanced methods you are using.
