# Insert chapter 6 title here

*Describe the work you have done this week and summarize your learning.*

- Describe your work and results clearly. 
- Assume the reader has an introductory course level understanding of writing and reading R code as well as statistical methods.
- Assume the reader has no previous knowledge of your data or the more advanced methods you are using.
```{r}
# Data wrangling 
#1 inout data, check their variable names, view the data contents and structures, and create some brief summaries of the variables
BPRS <- read.table("https://raw.githubusercontent.com/KimmoVehkalahti/MABS/master/Examples/data/BPRS.txt", sep  =" ", header = T)
RATS <- read.table("https://raw.githubusercontent.com/KimmoVehkalahti/MABS/master/Examples/data/rats.txt", header = TRUE, sep = '\t')
str(BPRS)
summary(BPRS)
str(RATS)
summary(RATS)
#2 Convert the categorical variables of both data sets to factors
library(dplyr)
library(tidyr)
# Factor variables ID and Group
RATS$ID <- factor(RATS$ID)
RATS$Group <- factor(RATS$Group)
BPRS$treatment <- factor(BPRS$treatment)
BPRS$subject <- factor(BPRS$subject)
#Convert the data sets to long form. Add a week variable to BPRS and a Time variable to RATS.
BPRSL <-  BPRS %>% 
  gather(key = weeks, value = bprs, -treatment, -subject)%>% 
  mutate(week = as.integer(substr(weeks,5,5)))
RATSL <- RATS %>%
  gather(key = WD, value = Weight, -ID, -Group) %>%
  mutate(Time = as.integer(substr(WD,3,4))) 
#glimpse two new dataset
glimpse(BPRSL)
glimpse(RATSL)

```

```{r}
#2. analysis
# Implement the analyses of Chapter 8 of MABS using the RATS data. 
# 2.1 Plot the RATSL data
library(ggplot2)
ggplot(RATSL, aes(x = Time, y = Weight, linetype = ID)) +
  geom_line() +
  scale_linetype_manual(values = rep(1:10, times=4)) +
  facet_grid(. ~ Group, labeller = label_both) +
  theme(legend.position = "none") + 
  scale_y_continuous(limits = c(min(RATSL$Weight), max(RATSL$Weight)))
# Standardise the variable bprs
RATSL_1 <- RATSL %>%
  group_by(Time) %>%
  mutate(stdweight = (Weight - mean(Weight))/sd(Weight) ) %>%
  ungroup()
# Glimpse the data
glimpse(RATSL_1)
# Plot again with the standardised bprs
ggplot(RATSL_1, aes(x =Time, y =stdweight, linetype =ID  )) +
  geom_line() +
  scale_linetype_manual(values = rep(1:10, times=4)) +
  facet_grid(. ~ Group, labeller = label_both) +
  scale_y_continuous(name = "standardized weight")
# Number of time, baseline  included
n <- RATSL_1$Time %>% unique() %>% length()
# Summary data with mean and standard error of bprs by treatment and week 
RATSL_1s<- RATSL_1 %>%
  group_by(Group, Time) %>%
  summarise( mean = mean(Weight), se = sd(Weight)/sqrt(n) ) %>%
  ungroup()
# Glimpse the data
glimpse(RATSL_1s)
# Plot the mean profiles
ggplot(RATSL_1s, aes(x = Time, y = mean, linetype = Group, shape = Group)) +
  geom_line() +
  scale_linetype_manual(values = c(1,2,3)) +
  geom_point(size=3) +
  scale_shape_manual(values = c(1,2,3)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se, linetype="1"), width=0.3) +
  theme(legend.position = c(0.8,0.8)) +
  scale_y_continuous(name = "mean(weight) +/- se(weight)")
# Draw a boxplot of the mean versus treatment
ggplot(RATSL_1s, aes(x = Group, y = mean)) +
  geom_boxplot() +
  stat_summary(fun.y = "mean", geom = "point", shape=23, size=4, fill = "white") +
  scale_y_continuous(name = "mean(weight), Times")
#comments: In these three gruops of rats, the the mean of weights of gruop1 is much lower than gruop2 and gruop3 counterpart.
#2.2 Implement the analyses of Chapter 9 of MABS using the BPRS data. 
# Plot the BPRSL data
dim(BPRSL)
ggplot(BPRSL, aes(x = week, y =bprs, linetype = subject)) +
  geom_line() +
  scale_linetype_manual(values = rep(1:10, times=4)) +
  facet_grid(. ~ treatment, labeller = label_both) +
  theme(legend.position = "none") + 
  scale_y_continuous(limits = c(min(BPRSL$bprs), max(BPRSL$bprs)))
BPRSL_reg <- lm(bprs ~ week + treatment, data = BPRSL)
summary(BPRSL_reg)
# access library lme4
library(lme4)
# Create a random intercept model
BPRSL_ref <- lmer(bprs ~ week + treatment + (1 | subject), data = BPRSL, REML = FALSE)
summary(BPRSL_ref)
# create a random intercept and random slope model
BPRSL_ref1 <- lmer(bprs ~ week + treatment + (week | subject), data = BPRSL, REML = FALSE)
summary(BPRSL_ref1)
anova(BPRSL_ref1, BPRSL_ref)
# create a random intercept and random slope model
BPRSL_ref2 <- lmer(bprs ~ week * treatment + (week | subject), data = BPRSL, REML = FALSE)
summary(BPRSL_ref2)
anova(BPRSL_ref1, BPRSL_ref2)
# Create a vector of the fitted values
Fitted <- fitted(BPRSL_ref2)
BPRSL2 <- BPRSL %>%
  mutate(Fitted)
ggplot(BPRSL2, aes(x = week, y =Fitted, linetype = subject)) +
  geom_line() +
  scale_linetype_manual(values = rep(1:10, times=4)) +
  facet_grid(. ~ treatment, labeller = label_both) +
  theme(legend.position = "none") + 
  scale_y_continuous(limits = c(min(BPRSL$bprs), max(BPRSL$bprs)))


```

